Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-05 manuscript.Rmd
null models final

by_model <- 
null_models %>% 
  mutate(model = c(rep("p", 5), rep("a", 5), rep("t", 5))
         ) %>% 
  group_by(model) %>% 
  nest()

map(by_model, specr::plot_variance)

fill_color <- "#377eb8"

@@

map(null_models2, performance::icc, by_group = TRUE)

@@

## save random effects
lapply(ranef(SAM1), write.table, 
       append = TRUE, 
       file = here::here("data", "raneff from SAM1 for TRT.csv"))

>>>>

@@

sjPlot::tab_model(null_models2[[1]],
                  null_models2[[2]],
                  null_models2[[3]], 
                  dv.labels = c("Personality", "Affect", "Thought"))

iccs <- 
map_dfr(null_models2, performance::icc, by_group = TRUE) %>% 
  mutate(model = c(rep("Personality", 3), 
                   rep("Affect", 3), 
                   rep("Thought", 3)),
         ICC = ICC*100)

iccs %>% 
  ggplot() +
  geom_col(aes(Group, ICC), fill = "#377eb8") +
  facet_wrap(~model) +
  theme_bw()
```

@@
